Quantifying the ease of viral escape from broad and narrow antibodies to influenza virus hemagglutinin

### 2017-10-05 paper/manuscript.tex
redraft of abstract
revised abstract again

\begin{abstract}
Nearly all viruses exhibit some antigenic variation.
However, the extent of this variation ranges widely across viruses and antibodies.
Influenza virus exhibits high antigenic variation, and can completely escape most neutralizing antibodies with single mutations.
However, some rare antibodies neutralize many influenza virus strains.
It is unclear how easily the virus might escape such broad antibodies if there was strong selection to do so.
Here we map all single amino-acid mutations to an H1 influenza hemagglutinin that increase resistance to several broad antibodies.
Crucially, our approach both identifies antigenic mutations and quantifies their effect size.
We find mutations that increase resistance to all antibodies tested, but the effect sizes range widely. 
Single mutations completely escape a broad antibody targeting the hemagglutinin receptor-binding pocket, similar to escape from narrow strain-specific antibodies.   
In contrast, the few mutations selected by broad antibodies targeting the hemagglutinin stalk have only small effects. 
Overall, our work demonstrates a method to quantify the ease of viral antibody escape, and shows that antibody breadth is not necessarily an indicator of the difficulty of viral escape.
%Instead, targeting a mutationally intolerant epitope in the stalk region seems to limit viral escape mutations to a few relatively ineffective options
\end{abstract}

\section*{INTRODUCTION}
Broadly neutralizing antibodies against influenza virus are of great interest... \cite{corti2017tackling}.

>>>>

\begin{abstract}
Influenza virus can completely escape most neutralizing antibodies with single mutations.
However, rare antibodies broadly neutralize many viral strains.
It is unclear how easily the virus might escape such broad antibodies if there was strong selection to do so.
Here we map all single amino-acid mutations to an H1 influenza hemagglutinin that increase resistance to several broad antibodies.
Crucially, our approach both identifies antigenic mutations and quantifies their effect size.
We find mutations that increase resistance to all antibodies tested, but the effect sizes range widely. 
Single mutations completely escape a broad antibody targeting the hemagglutinin receptor-binding pocket, similar to escape from narrow strain-specific antibodies.   
In contrast, the few mutations selected by broad antibodies targeting the hemagglutinin stalk have only small effects. 
Overall, our work demonstrates a method to quantify the ease of viral antibody escape, and shows that antibody breadth is not necessarily an indicator of the difficulty of viral escape.
In addition, our results show that broad antibodies targeting the hemagglutinin stalk are quantifiably harder to escape via point mutations.
\end{abstract}

\section*{INTRODUCTION}
Nearly all viruses exhibit some antigenic variation.
However, the extent of this variation ranges widely across viruses and antibodies.
Broadly neutralizing antibodies against influenza virus are of great interest... \cite{corti2017tackling}.
